\documentclass[12pt,-letter paper]{article}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\graphicspath{{figs/}}
\providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\begin{document}
\begin{enumerate}
\item write the number of all possible matrices of order \(2 \times 3\) with each entry  \(1\) or \(2\).
\item If $A=\myvec{1 & -2 & 3 \\ -4 & 2 & 5 }$ and $B=\myvec{2 & 3  \\ 4 & 5 \\ 2 & 1}$ and $BA=(b_{i,j})$, Find $b_{21}+b_{32}$.
\item if $\overrightarrow{a}=4,\overrightarrow{b}=3$ and $\overrightarrow{a},\overrightarrow{b}=6\sqrt{3}$,the nfind the value of $\overrightarrow{a}\times\overrightarrow{b}$

\item What are the coordinates of the point which is the reflection of the point \((\alpha, \beta, \gamma)\) in the XZ-plane?
\item write the value of $A=\myvec{a-b & b-c & c-a \\ b-c & c-a & a-b \\ c-a & a-b & b-c}$

\item Find the position vector of the point which divides the join of points with position $\overrightarrow{a}+3\overrightarrow{b}$ and $\overrightarrow{a} \cdot \overrightarrow{b}$ internally in the ratio 1: 3.

\item  On her birthday Seema decided to donate some money to children of an orphanage home. If there were 8 children less, every one would have got $\rupee10$ more. However, if there were 16 children more, every one would have got $\rupee10$ less. Using matrix method, find the number of children and the amount distributed by Seema. What values are reflected by Seema's decision?

\item Show that the function \( R(x) \) given by:
$
R(x) = 
\begin{cases} 
      \frac{e^{1/x} - 1}{e^{1/x} + 1}, & \text{if } x \neq 0, \\
      -1, & \text{if } x = 0 
\end{cases}
$
is discontinuous at \( x = 0 \).

\item Evaluate: 
$
\int_1^5 |x - 1| + |x - 2| + |x - 3| \, dx
$

\item Evaluate: 
$
\int_0^{\pi} \frac{x \sin x}{1 + 3\cos^2 x} \, dx
$

\item Find:$
\int (3x + 5)\sqrt{5} + 4x - 2x^2 \, dx
$
\item solve the differential equation :
	$ (x^2 + 3xy + y^2) \, dx - x^2 \, dy = 0 \, given \, that\,  y = 0, when \,  x = 1.$


\item  $solve for x$ : $\tan^{-1}\frac{2-x}{2+x}$=$\frac{1}{2}$ $\tan^{-1}\frac{x}{2}$, $x>0$
	
\item  prove that $2sin^-1\frac{3}{5}-tan^{-1}\frac{17}{31}=\frac{\pi}{4}$
\item A committee of $4$ students is selected at random from a group consisting of $7$ boys and $4$ girls. Find the probability that there are exactly $2$ boys in the committee, given that at least one girl must be there in the committee.
\item A random variable $X$ has the following probability distributio: \\\begin{table}[htb]
 \centering
  \begin{tabularx}{\textwidth}{|c|X|X|X|X|X|X|X|}
 \hline
 X & 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
  \hline
 P(X) & c & 2c & 2c & 3c & $c^2$ & $2c^2$ & $7c^2$+c \\
  \hline
  \end{tabularx}                                                   \end{table}\\
	Find the value of $c$ and also calculate mean of the distribution.
 \item Show that the lines $\frac{x-1}{3}=\frac{y-1}{-1}=\frac{z-1}{0}$ and$\frac{x-4}{2}=\frac{y}{0}=\frac{z+1}{3}$  intersect. Find their point of intersection.
\item $x=e^{cos2t}$ and $y=e^{sin2t}$,prove that $\frac{dy}{dx}=\frac{-ylogx}{xlogy}$.
\item verify mean value theorem for the function $f(x)=2sinx+sin2x$ on $[0,\pi]$.
\item Find the angle  between the vectors $\overrightarrow{a}+\overrightarrow{b}$ and $\overrightarrow{a}-\overrightarrow{b}$ if $\overrightarrow{a}=2\hat{i}-\hat{j}+3\hat{k}$ and $\overrightarrow{b}=3\hat{i}+\hat{j}-2\hat{k}$, and hence find a vector perpendicular to both $\overrightarrow{a}+\overrightarrow{b}$ and $\overrightarrow{a}-\overrightarrow{b}$.
\item Find the equation of the tangent line to the curve $y=\sqrt{5x-3}-5$, which is parallel to line $4x-2y+5=0$.
\item solve the differential equation : \\ $x\frac{dy}{dx}+y-x+xycotx=0 ; x\neq0$.
\item Find : $\int\frac{2x+1}{(x^2+1)(x^2+4)}dx$.
\item solve for $x$ : $\myvec{a+x & a-x & a-x \\ a-x & a+x & a-x \\ a-x & a-x & a+x }$ = 0, using properties of determinants.
\item using elementary row operations find the inverse of matrix $A$=$\myvec{3 & -3 & 4 \\ 2 & -3 & 4 \\ 0 & -1 & 1}$ and hence solve the following system of equations $3x-3y+4z=21,2x-3y+4z=20,-y+z=5$.
\item using integration, find the area of the angle formed by negative x-axis and tangent and normal to the circle $x^2+y^2=9$ at $(-1,2\sqrt{2})$.
\item A company manufactures two types of cardigans type A and type B. It costs \rupee360 to make a type A cardigan and \rupee120 to make a type B cardigan. The company can make at most $300$ cardigans and spend at most \rupee72,000 a day. The number of cardigans of type B cannot exceed the number of cardigans of type A by more than $200$. The company makes a profit of \rupee100 for each cardigan of type A and \rupee50 for every cardigan of type B.\\
Formulate this problem as a linear programming problem to maximise the profit to the company. Solve it graphically and find maximum profit.
\item A, B and C throw a pair of dice in that order alternately till one of them gets a total of $9$ and wins the game. Find their respective probabilities of winning. if A starts first.
\item Show that height of the cylinder of greatest volume which can be inscribed in a right circular cone of height h and semi-vertical angle a is one-third that of the cone and the greatest volume of the cylinder is $\frac{4}{27}\pi h^3 tan^2{\alpha}$.
\item Find the intervals in which the function $f(x)=\frac{4sinx}{2+cosx}-x; 0\leq x \leq 2\pi$ is strictly increasing or strictly decreasing.
\item Find the coordinates of the foot of perpendicular and perpendicular distance from the point $P(4 , 3 , 2 )$ to the plane $x+2y+3z=2$.Also find the image of P in the plane.
\item show that the relation $R$ defined by $(a,b)$ R $(c,d) \Rightarrow a+d=b+c$ on the $A\times A$,where $a=\{1,2,3,.....10\}$ is an equivaience relation.Hence write the equivalance class $[(3,4)] ;a,b,c,d \epsilon A$. 
\end{enumerate}
\end{document}


