\documentclass[12pt,-letter paper]{article}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\graphicspath{{figs/}}
\providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\begin{document}
\begin{enumerate}
\item Write the number of all possible matrices of order $2 \times 3$ with each entry  $1$ or $2$.
\item If $\vec(A)=\myvec{1 & -2 & 3 \\ -4 & 2 & 5 }$ and $\vec(B)=\myvec{2 & 3  \\ 4 & 5 \\ 2 & 1}$ and $\vec(BA)=(b_{ij})$, Find $b_{21}+b_{32}$.
\item If $\overset{\rightarrow}{a}=4,\overset{\rightarrow}{b}=3$ and $\overset{\rightarrow}{a},\overset{\rightarrow}{b}=6\sqrt{3}$, the find the value of $\overset{\rightarrow}{a}\times\overset{\rightarrow}{b}$

\item What are the coordinates of the point which is the reflection of the point $\brak{\alpha, \beta, \gamma}$ in the $XZ-plane$?
\item Write the value of $\vec(A)=\myvec{a-b & b-c & c-a \\ b-c & c-a & a-b \\ c-a & a-b & b-c}$

\item Find the position vector of the point which divides the join of points with position $\overset{\rightarrow}{a}+3\overset{\rightarrow}{b}$ and $\overset{\rightarrow}{a} \cdot \overset{\rightarrow}{b}$ internally in the ratio $1: 3$.

\item  On her birthday Seema decided to donate some money to children of an orphanage home. If there were $8$ children less, every one would have got \rupee$10$ more. However, if there were $16$ children more, every one would have got \rupee$10$ less. Using matrix method, find the number of children and the amount distributed by Seema. What values are reflected by Seema's decision?
\item Show that the function $f$ is given by:
$
f(x) =
\begin{cases}
    \frac{e^{1/x} - 1}{e^{1/x} + 1}, & \quad \text{if } x \neq 0, \\  
    0, & \quad \text{if } x = 0.
  \end{cases}
$
 is discontinuous at $x = 0$.  

\item Evaluate: 
	\begin{align*}
		\int_1^5 \mydet{x - 1} + \mydet{x - 2} + \mydet{x - 3} , dx
	\end{align*}

\item Evaluate: 
	\begin{align*}
		\int_0^{\pi} \frac{x \sin {x}}{1 + 3\cos^2 {x}} , dx
	\end{align*}

\item Find:
	\begin{align*}
	\int \brak{3x + 5}\sqrt{5} + 4x - 2x^2 , dx
	\end{align*}
\item Solve the differential equation :
	
	$ \brak{x^2 + 3xy + y^2} , dx - x^2 , dy = 0$ given that  $y = 0$, when  $x = 1.$


\item  Solve for
	\begin{align*}
		x : \tan^{-1}\frac{2-x}{2+x}=\frac{1}{2} \tan^{-1}\frac{x}{2}, x>0
\end{align*}
	
\item  Prove that $2\sin^{-1}\frac{3}{5}-\tan^{-1}\frac{17}{31}=\frac{\pi}{4}$
\item A committee of $4$ students is selected at random from a group consisting of $7$ boys and $4$ girls. Find the probability that there are exactly $2$ boys in the committee, given that at least one girl must be there in the committee.
\item A random variable $X$ has the following probability distributio: 
\begin{table}[htb]
 \centering
  \begin{tabularx}{\textwidth}{|c|X|X|X|X|X|X|X|}
 \hline
 X & 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
  \hline
 P(X) & c & 2c & 2c & 3c & $c^2$ & $2c^2$ & $7c^2$+c \\
  \hline
  \end{tabularx}
\end{table}\\
	Find the value of $c$ and also calculate mean of the distribution.
 \item Show that the lines $\frac{x-1}{3}=\frac{y-1}{-1}=\frac{z-1}{0}$ and$\frac{x-4}{2}=\frac{y}{0}=\frac{z+1}{3}$  intersect. Find their point of intersection.
 \item $x=e^{\cos{2t}}$ and $y=e^{\sin{2t}}$,prove that $\frac{dy}{dx}=\frac{-ylogx}{xlogy}$.
 \item Verify mean value theorem for the function $f\brak{x}=2\sin{x}+sin{2x}$ on $[0,\pi]$.
\item Find the angle  between the vectors $\overset{\rightarrow}{a}+\overset{\rightarrow}{b}$ and $\overset{\rightarrow}{a}-\overset{\rightarrow}{b}$ if $\overset{\rightarrow}{a}=2\hat{i}-\hat{j}+3\hat{k}$ and $\overset{\rightarrow}{b}=3\hat{i}+\hat{j}-2\hat{k}$, and hence find a vector perpendicular to both $\overset{\rightarrow}{a}+\overset{\rightarrow}{b}$ and $\overset{\rightarrow}{a}-\overset{\rightarrow}{b}$.
\item Find the equation of the tangent line to the curve $y=\sqrt{5x-3}-5$, which is parallel to line $4x-2y+5=0$.
\item Solve the differential equation :  $x\frac{dy}{dx}+y-x+xycotx=0 ; x\neq0$.
\item Find :\begin{align*}
		\int\frac{2x+1}{\brak{x^2+1}\brak{x^2+4}}dx
	\end{align*}.
\item Solve for $x$ : $\myvec{a+x & a-x & a-x \\ a-x & a+x & a-x \\ a-x & a-x & a+x }$ = 0, using properties of determinants.
\item Using elementary row operations find the inverse of matrix $\vec(A)$=$\myvec{3 & -3 & 4 \\ 2 & -3 & 4 \\ 0 & -1 & 1}$ and hence solve the following system of equations $3x-3y+4z=21,2x-3y+4z=20,-y+z=5$.
\item Using integration, find the area of the angle formed by negative x-axis and tangent and normal to the circle $x^2+y^2=9$ at $\brak{-1,2\sqrt{2}}$.
\item A company manufactures two types of cardigans type $A$ and type $B$. It costs \rupee$360$ to make a type $A$ cardigan and \rupee$120$ to make a type $B$ cardigan. The company can make at most $300$ cardigans and spend at most \rupee$72,000$ a day. The number of cardigans of type $B$ cannot exceed the number of cardigans of type $A$ by more than $200$. The company makes a profit of \rupee$100$ for each cardigan of type $A$ and \rupee$50$ for every cardigan of type $B$.
Formulate this problem as a linear programming problem to maximise the profit to the company. Solve it graphically and find maximum profit.
\item $A$, $B$ and $C$ throw a pair of dice in that order alternately till one of them gets a total of $9$ and wins the game. Find their respective probabilities of winning. if $A$ starts first.
\item Show that height of the cylinder of greatest volume which can be inscribed in a right circular cone of height $h$ and semi-vertical angle a is one-third that of the cone and the greatest volume of the cylinder is $\frac{4}{27}\pi h^3 tan^2{\alpha}$.
\item Find the intervals in which the function $f\brak{x}=\frac{4\sin{x}}{2+\cos{x}}-x; 0\leq x \leq 2\pi$ is strictly increasing or strictly decreasing.
\item Find the coordinates of the foot of perpendicular and perpendicular distance from the point $P\brak{4 , 3 , 2 }$ to the plane $x+2y+3z=2$.Also find the image of $P$ in the plane.
\item Show that the relation $R$ defined by $\brak{a,b}$ $R$ $\brak{c,d} \Rightarrow a+d=b+c$ on the $A\times A$,where $a$=$\cbrak{1,2,3,.....10}$ is an equivaience relation.Hence write the equivalance class $[\brak{3,}] ;a,b,c,d \epsilon A$.


\end{enumerate}
\end{document}


